\blue{...Numerical investigation of viscous flow instabilities through heterogeneous porous media using adaptive and unstructured meshes under different mobility scenarios...}

### 2017-07-03 Papers/ViscousInstabilities/article_figure1.tex
updates

%%%%
%%%%  FIGURE
%%%%
\begin{landscape}
\begin{figure}[ht] 
\vbox{\vspace{-1cm}
\hbox{\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_1.pdf}
      \includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_250_1.pdf}
      \includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_1000.pdf}}
\vspace{0.cm}
\hbox{\hspace{1.0cm} (a) pressure at t=0 \hspace{3.cm} (b) t=250\red{(???)} \hspace{3.0cm} (c) t=1000\red{(???)}}
\vspace{0.5cm}
\hbox{
      \includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_6000.pdf}
      \includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_end_1.pdf}}
\vspace{0.cm}
\hbox{ \hspace{2.cm} (d) t=6000\red{(???)} \hspace{3.cm} (e) t=XXX\red{(???)}}
\vspace{0.cm}
}   
\caption{Simulated flow in a Hele-Shaw cell ({\it VR}=10): (a) pressure profile $\left(\text{in g.cm}^{-1}\text{.s}^{-2}\right)$ with source and sink regions explicitly shown along with dimensions (in cm); (b-e) snapshots of wetting phase saturation showing flow profile as the simulation evolves. The domain contains $47000$ \PN[1]{2} triangular elements. The pressure and saturation range of values are the same like the  case in fig.\ref{fig:homoheleshaw_VN3}.}
\label{fig:homoheleshaw_VN10}
\end{figure}
\end{landscape}
\clearpage
\end{comment}

%%%
%%% FIGURE XXXXXX
%%%
\begin{landscape}
  \begin{figure}[ht]
  \vbox{\vspace{-1cm}
      \hbox{\includegraphics[width=.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_1.pdf}
            \includegraphics[width=.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_500.pdf} 
            \includegraphics[width=.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_2000.pdf} }
      \hbox{\hspace{1.0cm} (a) permeability map \hspace{3.cm} (b) t=0.75s \hspace{4.0cm} (c) t=8s}
      \vspace{0.5cm}
      \hbox{\includegraphics[width=.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_3000.pdf}
            \includegraphics[width=.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_6000.pdf}
            \includegraphics[width=.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_24000.pdf} }
      \hbox{\hspace{2.5cm} (d) t=18s \hspace{5.cm} (e) t= \hspace{3.0cm} (f) t=24000 }}
\caption{Simulated flow in a modified Hele-Shaw cell with {\it VR}=10: (a) permeability distribution $\left(\text{10}^{-10}\le\mathbf{K}_{1}\le\text{5}\times\text{10}^{-10}\right.$, {\bf K}$_{2}$=10$^{-10}$, 10$^{-11}\le\mathbf{K}_{3}\le$ 5$\times$10$^{-10}$ and 10$^{-12}\le\mathbf{K}_{4}\le$ 5$\times$10$\left.^{-10}\text{ cm}^{2}\right)$; (b-f) snapshots of saturation profile during \red{XX} seconds of simulation. The domain contains \red{XX} \PN[1]{2} element-pairs.}
\label{fig:HeleShawHeter_VR10}
\end{figure}
\end{landscape}
\clearpage

>>>>

%%%%
%%%%  FIGURE
%%%%
\begin{landscape}
\begin{figure}[ht] 
\vbox{\vspace{-1cm}
\hbox{\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_1.pdf}
      \includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_250_1.pdf}
      \includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_1000.pdf}}
\vspace{0.cm}
\hbox{\hspace{1.0cm} (a) pressure at t=0 \hspace{3.cm} (b) t=250\red{(???)} \hspace{3.0cm} (c) t=1000\red{(???)}}
\vspace{0.5cm}
\hbox{
      \includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_6000.pdf}
      \includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_end_1.pdf}}
\vspace{0.cm}
\hbox{ \hspace{2.cm} (d) t=6000\red{(???)} \hspace{3.cm} (e) t=XXX\red{(???)}}
\vspace{0.cm}
}   
\caption{Simulated flow in a Hele-Shaw cell ({\it VR}=10): (a) pressure profile $\left(\text{in g.cm}^{-1}\text{.s}^{-2}\right)$ with source and sink regions explicitly shown along with dimensions (in cm); (b-e) snapshots of wetting phase saturation showing flow profile as the simulation evolves. The domain contains $47000$ \PN[1]{2} triangular elements. The pressure and saturation range of values are the same like the  case in fig.\ref{fig:homoheleshaw_VN3}.}
\label{fig:homoheleshaw_VN10}
\end{figure}
\end{landscape}
\clearpage

%%%
%%% FIGURE XXXXXX
%%%
\begin{landscape}
  \begin{figure}[ht]
  \vbox{\vspace{-1cm}
      \hbox{\includegraphics[width=.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_1.pdf}
            \includegraphics[width=.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_500.pdf} 
            \includegraphics[width=.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_2000.pdf} }
      \hbox{\hspace{1.0cm} (a) permeability map \hspace{3.cm} (b) t=0.75s \hspace{4.0cm} (c) t=8s}
      \vspace{0.5cm}
      \hbox{\includegraphics[width=.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_3000.pdf}
            \includegraphics[width=.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_6000.pdf}
            \includegraphics[width=.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_24000.pdf} }
      \hbox{\hspace{2.5cm} (d) t=18s \hspace{5.cm} (e) t= \hspace{3.0cm} (f) t=24000 }}
\caption{Simulated flow in a modified Hele-Shaw cell with {\it VR}=10: (a) permeability distribution $\left(\text{10}^{-10}\le\mathbf{K}_{1}\le\text{5}\times\text{10}^{-10}\right.$, {\bf K}$_{2}$=10$^{-10}$, 10$^{-11}\le\mathbf{K}_{3}\le$ 5$\times$10$^{-10}$ and 10$^{-12}\le\mathbf{K}_{4}\le$ 5$\times$10$\left.^{-10}\text{ cm}^{2}\right)$; (b-f) snapshots of saturation profile during \red{XX} seconds of simulation. The domain contains 26313 \PN[1]{2} element-pairs.}
\label{fig:HeleShawHeter_VR10}
\end{figure}
\end{landscape}
\clearpage
\end{comment}

%%%
%%% FIGURE XXXXXX
%%%
\begin{landscape}
  \begin{figure}[ht]
  \vbox{\vspace{-.5cm}
      \hbox{\includegraphics[width=.4\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_1}
            \includegraphics[width=.55\textwidth, height=.4\textwidth]{./Pics1/Saffman_heterogeneous_VR10/ST_Heterog_VR10_D200Hb} 
            \includegraphics[width=.42\textwidth]{./Pics1/Saffman_heterogeneous_VR10/ST_Heterog_VR10_D900Hb} }
      \hbox{\hspace{1.0cm} (a) permeability map \hspace{3.cm} (b) t=0.19s \hspace{4.0cm} (c) t=0.63s}
      \vspace{0.5cm}
      \hbox{\includegraphics[width=.42\textwidth]{./Pics1/Saffman_heterogeneous_VR10/ST_Heterog_VR10_D5000Hb.pdf}
            \includegraphics[width=.42\textwidth]{./Pics1/Saffman_heterogeneous_VR10/ST_Heterog_VR10_D8000Hb.pdf}
            \includegraphics[width=.42\textwidth]{./Pics1/Saffman_heterogeneous_VR10/ST_Heterog_VR10_D13800Hb.pdf} }
      \hbox{\hspace{2.5cm} (d) t=3.41ss \hspace{5.cm} (e) t= 5.54s\hspace{3.0cm} (f) t=9.77s }}
\caption{Simulated flow in a modified Hele-Shaw cell with {\it VR}=10: (a) permeability distribution $\left(\text{10}^{-10}\le\mathbf{K}_{1}\le\text{5}\times\text{10}^{-10}\right.$, {\bf K}$_{2}$=10$^{-10}$, 10$^{-11}\le\mathbf{K}_{3}\le$ 5$\times$10$^{-10}$ and 10$^{-12}\le\mathbf{K}_{4}\le$ 5$\times$10$\left.^{-10}\text{ cm}^{2}\right)$; (b-f) snapshots of saturation profile during 9.77 seconds of simulation. The domain contains 26313 \PN[1]{2} element-pairs.}
\label{fig:HeleShawHeter_VR10}
\end{figure}
\end{landscape}
\clearpage
